### 2017-10-04 Documents/bootcamp_topic_pandas-input.tex
Pands 1 outline update

%%%%%%%%%%%%%%%%%%%%%%Headers and Footers%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagestyle{headandfoot}
\runningheadrule
\firstpageheadrule
\firstpageheader{\includegraphics[width=0.25\textwidth]{../Figures/stern_black1.pdf}}{}{Data Bootcamp: Python Fundementals 1}
\runningheader{}{}{}
\runningfooter{}{}{}

@@

\bigskip\bigskip
\centerline{\Large \bf Topic Outline:  Python Fundamentals 2}
\medskip
\centerline{Revised: \today}

@@

\begin{itemize}
\item  Today's handouts:  this outline, stickers
\item  All posted on {\it Topic outlines \& book \& links\/} page of website (except the stickers).
\end{itemize}

@@

\begin{itemize}

\item Tools and buzzwords
\begin{itemize}
\item Boolean variables, comparisons, conditionals ({\tt if}, {\tt else}), slicing,
loops ({\tt for}), function definitions.
\end{itemize}

@@

\item What is this?
\begin{itemize}
\item \verb|'abcd' |
\item \verb|['Chase', 'Dave', 'Sarah', 'Spencer'] |
\item \verb|('Chase', 'Dave', 'Sarah', 'Spencer') |
\item \verb|'98.76'|
\item \verb|float('98.76')|
\item \verb|int(float('98.76'))|
\item \verb|len('98.76')|
\item \verb|list('abcd')|
\item Tab completion
\item {\tt object.method?}
\item Object inspector
\end{itemize}

\item {\bf Exercise}
\begin{itemize}
\item Put red sticker on your laptop
\item Start Spyder
\item Open new file  \verb|bootcamp_class_pyfun2.py|
in your \verb|Data_Bootcamp| directory
\item Replace red sticker with green when you're set
\end{itemize}

@@

\section*{Python fundamentals 2}

We'll follow the book chapter.
\begin{itemize}
\item Dictionaries
\item Logical expressions (comparisons)
\item Conditionals
\item Slicing strings and lists
\item Loops over lists and strings ({\tt for}, {\tt else})
\item Loops over counters ({\tt range()})
\item Defining functions
\item Style
\item Review
\begin{itemize}
\item Put red sticker on, replace with green when done
\end{itemize}
\end{itemize}

@@

\section*{After this module}

\begin{itemize}
\item Required
\begin{itemize}
%\item Review this chapter
\item Code Practice \#2 (should take about an hour)
\end{itemize}
\item Recommended
\begin{itemize}
\item {\bf Write}:  After class, write down everything you remember without using your notes
\item {\bf Review:} Reread the chapter and fill in anything you missed.
\item Ask for help if you get stuck.
\end{itemize}
\end{itemize}

>>>>

%%%%%%%%%%%%%%%%%%%%%%Headers and Footers%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagestyle{headandfoot}
\runningheadrule
\firstpageheadrule
\firstpageheader{\includegraphics[width=0.25\textwidth]{../Figures/stern_black1.pdf}}{}{Data Bootcamp: Pandas 1}
\runningheader{}{}{}
\runningfooter{}{}{}

@@

\bigskip\bigskip
\centerline{\Large \bf Topic Outline:  Pandas 1:  Data Input}
\medskip
\centerline{Revised: \today}

@@

\begin{itemize}
\item  Today's handouts:  this outline
\item  All posted on {\it Topic outlines \& links\/} page of website (except the stickers).
\end{itemize}

@@

\begin{itemize}
\item Tools and buzzwords
\begin{itemize}
\item Packages, import, dataframe, csv files, series, columns, index, API.
\end{itemize}

@@

\item What is this?
\begin{itemize}
\item \verb|x = 'abcd'|
\item \verb|x[1]|
\item \verb|'abcd'[1]|
\item \verb|['x1', 'x2']|
\item \verb|d = {'x1': [1, 5, 3], 'x2': [7, 2, 4]}|
\item \verb|d['x1']|
\item \verb|1 > 0|
\item \verb|type(1>0)|
\item Tab completion
\item {\tt object.method?}
\item Function returns
\item Objects and methods
\end{itemize}

\item {\bf Exercise}
\begin{itemize}
\item Put red sticker on your laptop
\item Start Spyder
\item Open blank file \verb|bootcamp_pandas1.py| to use in class
\item For second half:  save Python code file in your \verb|Data_Bootcamp| directory: \\
GitHub $\Rightarrow$ Code $\Rightarrow$ Python $\Rightarrow$ \verb|bootcamp_pandas-input.py|
$\Rightarrow$ click on Raw button
\item Raise your hand if you're stuck
\item Replace red sticker with green when you're set
\end{itemize}

@@

\section*{Pandas 1: Data input}

We'll follow the book chapter.
\begin{itemize}
\item Packages
\item Importing packages
\item Properties of dataframes
\item Working with variables
\item Dataframe methods
\item Reading files from your computer
\item Reading internet files
\item Examples:  Penn World Table, World Economic Outlook, PISA education data, UN population data and
projections, income by college major
\item APIs:  FRED, World Bank, Fama-French equity returns
\item Review
\begin{itemize}
\item Put red sticker on, replace with green when done
\end{itemize}
\end{itemize}

@@

\section*{After class}

\begin{itemize}
\item Required
\begin{itemize}
\item Review this chapter
\item Code Practice \#3 (due October 20th)\\
Submit hardcopy of code file \\
Code template:  GitHub $\Rightarrow$ Code $\Rightarrow$ Python
$\Rightarrow$ \verb|bootcamp_practice_3_template.py|

\end{itemize}
\item Recommended (always)
\begin{itemize}
\item {\bf Write}:  After class, write down everything you remember without using your notes
\item {\bf Review:} Reread the chapter and fill in anything you missed.
\item Ask for help if you get stuck.
\end{itemize}
\end{itemize}
